Introductory statistics with `intRo`

### 2016-02-11 jcgs-paper-2016/paper.Rmd
Some small changes

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{sec:extensible} and section \ref{modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.

@@

## Exciting
In general, introduction to statistics is a class undergraduate students dread. It's hard, the vocabulary is unfamiliar, and the software is difficult to use. With \texttt{intRo}, we hope to flip this paradigm. \texttt{intRo} is a fun, easy to use tool that's available on the web, and is also usable on mobile devices. As a web-based application, this tool is immediately more familiar to students than a desktop application. With interactive plots from \texttt{ggvis} [@ggvis], \texttt{intRo} brings a `wow'-factor to learning introductory statistics.

Once students get pulled in by an easy to use interface and fun interaction with their data, \texttt{intRo} has an ulterior motive: to get students excited about programming. By navigating about the user interface of \texttt{intRo}, students are actually creating a fully-executable \texttt{R} script that they can download and run locally as well as viewing the script change real-time within the application. This code creation element of \texttt{intRo} is meant to generate excitement about programming in \texttt{R} and empower students to feel that they can generate code as well. \texttt{intRo} uses \texttt{rmarkdown}'s [@rmarkdown] \texttt{render} function in order to print the results, by dymanically executing the user's \texttt{R} script. By default, the output will include the \texttt{R} code, but if the user elects to hide the source code by clicking the code toggle button at the top, the code will not appear in the printed results.

## Extensible
\label{sec:extensible}
On the front end, user interaction with \texttt{intRo} is split into bitesize chunks that we call modules. Modules are self-contained pieces of functionality which implement common statistical procedures that are often used in introductory statistics classes.

@@

# Understand intRo

>>>>

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.

@@

\texttt{intRo} has an ulterior motive as well: to get students excited about programming. By navigating about the user interface of \texttt{intRo}, students are actually creating a fully-executable \texttt{R} script that they can download and run locally as well as viewing the script change real-time within the application. This code creation element of \texttt{intRo} is meant to generate excitement about programming in \texttt{R} and empower students to feel that they can generate code as well. \texttt{intRo} uses \texttt{rmarkdown}'s [@rmarkdown] \texttt{render} function in order to print the results, by dymanically executing the user's \texttt{R} script. By default, the output will include the \texttt{R} code, but if the user elects to hide the source code by clicking the code toggle button at the top, the code will not appear in the printed results.

On the front end, user interaction with \texttt{intRo} is split into bitesize chunks that we call modules. Modules are self-contained pieces of functionality which implement common statistical procedures that are often used in introductory statistics classes.

@@

# Understanding intRo
